---
title: "Homework1"
output: pdf_document
date: "`r Sys.Date()`"
---

```{r}
#options(tinytex.verbose = TRUE)
```


### Question 1

Suppose a lab instrument loses 12 of its value each year. Its current value is 1800. Compute its value after
4 years

```{r }
V = 1800*(1-0.12)^4

```

### Question 3
Create a vector of temperatures using :
72, 75, 71, 68, 70, 74, 77, 73.
Then use indexing to extract:
1. the first temperature,
2. the last three temperatures,
3. all temperatures except the fourth,
4. all temperatures at least 74.

```{r, echo=FALSE}
temperature = c(72,75,71,68,70,74,77,73)
# the first temperature
temperature[c(1)]
# the last three temperature
temperature[c(6:8)]
# all temperatures except the fourth
temperature[c(-4)]
# all temperature at least 74
temperature>=74 # need to change this

```

### Question 4
Let
x = 2, 4, 6, 8, 10.

Create this vector in R. Then compute:
$x^2$
$x + 5$,
$\sqrt{x}$,
a data frame with columns x, .

```{r}
x = c(2,4,6,8,10)
# x squared
x_squared = x^2
# x plus five
x_plus_five <- x + 5;
# square root of x
sqrt_x = sqrt(x)

```