---
title: "Homework I"
output: pdf_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions

Show your code and the resulting output. Please ensure that your submission is clearly organized, readable, and easy to follow.


## Question 1: 

Suppose a lab instrument loses 12% of its value each year. Its current value is
\$1800. Compute its value after 4 years:

\[
V = 1800(1 - 0.12)^4.
\]

```{r}
V = 1800*(1 -0.12)^4
cat(sprintf("The value after 4 years is %.5f", V))
```


## Question 2: 

A medication dose is calculated from a patient's weight using

\[
\text{dose} = 0.8 \times \text{weight in kg}.
\]

Create R objects named `weight_lb`, `kg_per_lb`, and `dose_rate`.

Use these values:

\[
\text{weight\_lb} = 165, \quad \text{kg\_per\_lb} = 0.453592, \quad \text{dose\_rate} = 0.8.
\]

Convert the weight to kilograms, compute the dose, and print the dose rounded to one decimal place.

```{r}
weight_lb <- 165
kg_per_lb <- 0.453592
dose_rate <- 0.8
weight_in_kg <- weight_lb*kg_per_lb
dose <- dose_rate*weight_in_kg
cat(sprintf("The dose rate is $%.1f", dose))
```


## Question 3

Create a vector of temperatures using `c()`:

\[
72, 75, 71, 68, 70, 74, 77, 73.
\]

Then use indexing to extract:

1. the first temperature,
2. the last three temperatures,
3. all temperatures except the fourth,
4. all temperatures at least 74.

```{r}
temperatures <- c(72, 75, 71, 68, 70, 74, 77, 73)
cat(sprintf("The first temperature is %d", temperatures[c(1)]))
cat("\n The last three temperatures are ", temperatures[c(6:8)])
cat("\n All temperature except the fourth  ", temperatures[c(-4)])
cat("\n All temperatures at least 74 ", temperatures>=74)
```


## Question 4

Let

\[
x = 2, 4, 6, 8, 10.
\]

Create this vector. Then compute:

1. \(x^2\),
2. \(x + 5\),
3. \(\sqrt{x}\),
4. a matrix with columns `x`, `x_squared`, and `sqrt_x`.
```{r}
x <- c(2,4,6,8,10)
x_squared <- x^2
cat("\n The square of x ", x_squared)

x_plus_5 <- x + 5
cat("x plus five is ", x_plus_5)

sqrt_x <- sqrt(x)
cat("\n The square root of x", sqrt_x)

mat_x <- cbind(x, x_squared, sqrt_x)
#cat("\n The matrix of x", mat_x)
print(mat_x)
```
