---
title: "Homework III"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions

Show your code and the resulting output. Please ensure that your submission is clearly organized, readable, and easy to follow.


## Question 1: 

Use Latin Hypercube sample and independent and identically distributed (iid) sample from U(0,1) to approximate the integration of
\[
f(x_1, x_2)=\log\left(1/\sqrt{x_1}+1/\sqrt{x_2}\right)
\]
on $[0,1]^2$. Note: Let
\[
\mu=\int^1_0\int^1_0 f(x_1, x_2) dx_1 dx_2=1.25
\]
Compare the estimates and provide brief comments.

Hints: You may follow the steps below:

1. Develop a function that can generate two dimensional Latin Hypercube samples.
```{r}
two_dim_latin_hypercube <- function(n){
  x <- sample(1:n)
  x <- x - runif(n)
  x1 <- x/n 
  x2 <- x/n
  cbind(x1, x2) # the value of x1 and x2 are the same here
}

two_dim_latin_hypercube1 <- function(n){
  x1 <- sample(1:n) - runif(n) # this gives big numbers
  x2 <- sample(1:n) - runif(n)
  x1 <- x1/n
  x2 <- x2/n
  cbind(x1, x2)
}

two_dim_latin_hypercube1(10)
 
```


2. Develop a function that can generate two dimensional iid uniform samples.
```{r}
# a function that generate two dimensional iid uniform samples
iid_unif_samples <- function(n){
  x1 <- runif(n)
  x2 <- runif(n)
  cbind(x1, x2)
}
iid_unif_samples(10)
```

3. Develop a function that can approximate $\int^1_0\int^1_0 f(x_1, x_2) dx_1 dx_2$ using a given sample.
```{r}
two.dim.log.fun <- function(x1, x2){
  
  log(1/sqrt(x1) + 1/sqrt(x2))
}

approx.int.log.fun <- function(x1, x2){
  
}

```


4. plug in the output of the function in 1  to the function you developed in 3. You can get an approximation of $\int^1_0\int^1_0 f(x_1, x_2) dx_1 dx_2$ using Latin hypercube samples.

5. plug in the output of function in 2
to the function in 3.  You can get an approximation of $\int^1_0\int^1_0 f(x_1, x_2) dx_1 dx_2$ using iid uniform samples. 

6. How far is your approximation from the true value? Which method (lhs and iid) is closer to the true value?
If you repeat 4 and 5, will the result change?

7. Replicate 4 and 5 for nrep times. 
You will have nrep approximations from each method. Let
\[
\hat\mu^{lhs}_1, \ldots, \hat\mu^{lhs}_{nrep}
\]
and
\[
\hat\mu^{iid}_1, \ldots, \hat\mu^{iid}_{nrep}
\]
be the resulting approximations. Compute the sample bias:
\[
\frac{1}{nrep}\sum^{nrep}_{i=1}\hat\mu^{iid}_i-\mu
\]
\[
\frac{1}{nrep}\sum^{nrep}_{i=1}\hat\mu^{lhs}_i-\mu
\]
the sample variances:
\[
\frac{1}{nrep-1}\sum^{nrep}_{i=1}\left(\hat\mu^{iid}_i-\frac{1}{nrep}\sum^{nrep}_{j=1}\hat\mu^{iid}_j\right)^2
\]
\[
\frac{1}{nrep-1}\sum^{nrep}_{i=1}\left(\hat\mu^{lhs}_i-\frac{1}{nrep}\sum^{nrep}_{j=1}\hat\mu^{lhs}_j\right)^2
\]
and the mean squared errors:
\[
\frac{1}{nrep}\sum^{nrep}_{i=1}\left(\hat\mu^{iid}_i-\mu\right)^2
\]
\[
\frac{1}{nrep}\sum^{nrep}_{i=1}\left(\hat\mu^{lhs}_i-\mu\right)^2
\]

8. Try different $n$. Comment on how is the result change over $n$.

```{r}
# Your code here
```






## Question 2: 
Use simulation to estimate the 90th
percentile of the distance between two points (say, $(x_1, y_1)$ and $(x_2, y_2)$ )chosen at random in the interior of a unit square (i.e., $[0,1]^2$).

```{r}
# Your code here
```


## Question 3:

Use the ``Bschool.csv'' dataset to find the answers of the following question within this dataset. Note: Use the pipe operator and functions in tidyverse packages this time. 

1. Which professor rank (i.e., associate, assistant, or professor) has the highest average teaching evaluation score?
```{r}
bschool <- read.csv("C:/Users/FRT/Downloads/Fall-2026/MATH-8830/Dataset/Bschool.csv")
head(bschool)
```


```{r}
library('dplyr')
mean_score <- tapply(Bschool$score, Bschool$title, mean)
highest <- max(mean_score)
cat("The professor who has the higher rank", highest)
bschool |> filter(title=="Professor")|>
          mean(score)
```

2. What is the number of female associate professors? 

3. Is median teaching evaluation score in fall semester  higher than that in spring semester?

```{r}

```